---
title: "Fwd_contact_tracing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warnings=FALSE, out.width='1000px', dpi=300, message=FALSE)
rm(list=ls())
library(ggplot2)
library(dplyr)
library(tidyr)
library(reshape2)
library(cowplot)
library(knitr)
library(forcats)
library(bigsnpr)
library(RColorBrewer)
```
If we assume that an index case in a school has a chance of transmitting at all that is characterized by over dispersion (which follows a negative binomial distribution with parameter k=0.1) coupled with if they transmit, then they only show symptoms with a probability of 21% (which follows a binomial distribution) we can get the distribution of expected observed transmissions through forward contact_tracing
```{r}
# Distribution of number of secondary infections if each case has N contacts
n_cases<-200
R0<-1.1
n_contacts_per_case<-10 # This needs to be high enough to ensure upper bound of number infected is incorporated
n_traced<-n_cases*n_contacts_per_case
k <-0.1
n_runs<-20
#How many people does the index case transmit to?
mu = R0
n_transmissions_per_case<-rnbinom(n=n_cases, mu= R0, size = k)
hist(n_transmissions_per_case)
# On average how many secondary infections are there? (should be ~2.5)
mean_secondary_inf<-sum(n_transmissions_per_case)/n_cases
mean_prob_of_transmission_per_contact<- 100*sum(n_transmissions_per_case)/n_traced
prob_of_transmission_per_contact<-100*n_transmissions_per_case/n_contacts_per_case
hist(prob_of_transmission_per_contact, br=seq(-0.5,max(prob_of_transmission_per_contact+1),by=1) )

#What % of cases transmit onwards?
pct_cases_that_transmit<-100*sum(n_transmissions_per_case>0)/n_cases

# From those that get infected, how many show symptoms (i.e. how many would be detected transmissions)?
pct_symptomatic = 0.21
n_symptoms_per_case<-rbinom(n = n_cases, size = n_transmissions_per_case, prob = pct_symptomatic)
hist(n_symptoms_per_case, breaks = 25)
expected_number_with_symptoms_per_case    <-    sum(n_symptoms_per_case)/n_cases
mean_prob_of_symptoms_per_contact         <-100*sum(n_symptoms_per_case)/n_traced
prob_of_detecting_transmission_per_contact<-100*    n_symptoms_per_case /n_contacts_per_case
hist(prob_of_detecting_transmission_per_contact, breaks = 25)

 # What % of cases transmit onwards AND that transmission is detected?
pct_cases_that_transmission_detected<-100*sum(n_symptoms_per_case>0)/n_cases

```
Write a function that takes as an input k, n_contacts, % symptomatic, and R0 and spits out the chance of observing a transmission (symptomatic to symptomatic) per case and per contact
```{r}
forward_tracing<-function(k, n_contacts_per_case, R0, pct_symptomatic){
  n_cases<-200
  n_traced<-n_cases*n_contacts_per_case
  mu = R0
  #How many people does the index case transmit to?
  n_transmissions_per_case<-rnbinom(n=n_cases, mu= R0, size = k)
  mean_prob_of_transmission_per_contact<- 100*sum(n_transmissions_per_case)/n_traced
  prob_of_transmission_per_contact<-100*n_transmissions_per_case/n_contacts_per_case
  # What % of cases transmit onwards?
  pct_cases_that_transmit<-100*sum(n_transmissions_per_case>1)/n_cases

 # How many of these would be detected?
  n_symptoms_per_case<-rbinom(n = n_cases, size = n_transmissions_per_case, prob = pct_symptomatic)
  
  # What % of cases transmit onwards AND that transmission is detected?
  pct_cases_that_transmission_detected<-100*sum(n_symptoms_per_case>0)/n_cases
  
  expected_number_with_symptoms_per_case    <-    sum(n_symptoms_per_case)/n_cases
  mean_prob_of_symptoms_per_contact         <-100*sum(n_symptoms_per_case)/n_traced
  
  
  
  output<-c(pct_cases_that_transmit, pct_cases_that_transmission_detected, mean_prob_of_symptoms_per_contact)
  return(output)
  
}

linspace <- function(x1, x2, n=100) {
  stopifnot(is.numeric(x1), is.numeric(x2), length(x1)==1, length(x2)==1)
  n <- floor(n)
  if (n <= 1) x2
  else seq(x1, x2, length.out=n)
}

#replicate(1000, get_percent_symptomatic(2.5, 0.1, 0.21, 20)) %>% quantile(probs = c(0.025, 0.5, 0.975))
```

Pick 3 k values and vary percent symptomatic, find pct of cases with detected transmission
```{r}
psymvec<-linspace(0, 1, n=19)
R0<-2.5
kvec<-c(0.05, 0.1, 0.2) # 95% CI from Endo et al
nsamps<-1000

for (i in 1:length(kvec)){
  k<-kvec[i]
  ks<-rep(k, length(psymvec))
  pct_det_transmission_med<-rep(0, length(psymvec))
  pct_det_transmission_lb<-rep(0, length(psymvec))
  pct_det_transmission_ub<-rep(0, length(psymvec))
  for(j in 1:length(psymvec)){
    pct_symptomatic<-psymvec[j]
    pct_det<-rep(0, nsamps)
    for (m in 1:nsamps){
    out<-forward_tracing(k, n_contacts_per_case, R0, pct_symptomatic)
    pct_det[m]<- out[2]
    }
    pct_det_transmission_med[j]<-as.numeric(quantile(pct_det, 0.5))
    pct_det_transmission_lb[j]<-as.numeric(quantile(pct_det, 0.025))
    pct_det_transmission_ub[j]<-as.numeric(quantile(pct_det, 0.975))
  }
  if(i==1){
    df<- data.frame(psymvec,ks, pct_det_transmission_med, pct_det_transmission_lb,pct_det_transmission_ub)
  }
  else{
    dfi<- data.frame(psymvec,ks, pct_det_transmission_med, pct_det_transmission_lb,pct_det_transmission_ub)
    df<-rbind(df,dfi)
  }
  
}
```
```{r}
wd<-getwd()
path =paste0(wd,"/fwd_tracing.png")
plt<-ggplot(df) + geom_line(aes(x = 100*psymvec, y = pct_det_transmission_med, color = factor(ks)))  + scale_color_brewer(palette = "Set2")+
  geom_ribbon(aes(x = 100*psymvec, ymin = pct_det_transmission_lb, ymax = pct_det_transmission_ub, fill= factor(ks)), alpha = 0.1)+ scale_color_brewer(palette = "Set2") + scale_fill_brewer(palette = "Set2") + geom_vline(xintercept = 21, linetype = "dashed") + geom_vline(xintercept = 70) + xlab('Percent symptomatic') + ylab('% of index cases with detected transmission') +  theme(legend.position = "right") + coord_cartesian(ylim = c(0, 50))
# geom_point(x = 0.21, y = 2.6, shape = "*", size = 6)+
plt
ggsave(filename = path, device = "png", dpi = 1000, width = 7, height = 5, units="in")
k = 0.1
# Children scenario
pct_det<-rep(0, nsamps)
    for (m in 1:nsamps){
    out<-forward_tracing(k, n_contacts_per_case, R0, 0.21)
    pct_det[m]<- out[2]
    }
    pct_det_transmission_med<-as.numeric(quantile(pct_det, 0.5))
    pct_det_transmission_lb<-as.numeric(quantile(pct_det, 0.025))
    pct_det_transmission_ub<-as.numeric(quantile(pct_det, 0.975))
```



